% 07_discussion.tex — Discussion
\section{Discussion}
\label{sec:discussion}

\subsection{Interpretation of Results}

The experimental results validate the central thesis: coupled decision problems with heterogeneous knowledge require an integrated approach that simultaneously addresses lever coupling, knowledge heterogeneity, and the cognitive assembly bottleneck.
The ablation study provides direct evidence---removing any single component degrades at least precision or recall of intervention discovery.

The encoding layer's contribution is particularly evident in cross-type query performance, where the gap between the full system (\CROSSTYPEACCURACY{}) and raw concatenation (\RAWCONCATACCURACY{}) demonstrates that preserving epistemic metadata is essential for cross-source reasoning.
Conflicts between knowledge sources---such as expert judgment contradicting quantitative analysis on promotion effectiveness---become diagnostic signals when encoded properly, rather than ambiguous noise in concatenated text.

\subsection{Pipeline Efficiency}

The progressive reduction pipeline achieves a compression ratio of approximately $10^{17}$:1 while maintaining complete ground-truth coverage.
This efficiency arises from the complementary analytical dimensions of the diagnostic agents: each agent prunes along a different axis (sensitivity, interaction, feasibility, temporality, portfolio effects), and their combined pruning is multiplicative rather than additive.

\subsection{Limitations}

Several limitations should be noted:
\begin{enumerate}
    \item \textbf{Synthetic data}: While the BevCo scenario embeds realistic correlations and interaction effects, real-world RGM data exhibits additional complexities including missing data, measurement error, and temporal non-stationarity that our synthetic generator does not fully capture.
    \item \textbf{Scale}: The current implementation runs sequentially for determinism; production deployment would benefit from true parallel agent execution.
    \item \textbf{Expert encoding}: The temporal belief encoding assumes expert statements can be decomposed into lever-direction-magnitude triples, which may oversimplify nuanced qualitative knowledge.
    \item \textbf{Ground truth}: The planted interaction effects, while representative, cover a limited subset of possible coupling patterns.
\end{enumerate}

\subsection{What the Ablation Reveals}

The ablation study reveals an important asymmetry: removing the coupling model primarily affects \emph{what} the system discovers (which effects), while removing the encoding primarily affects \emph{how well} the system reasons (precision of interventions), and removing the pipeline primarily affects \emph{how efficiently} the system explores (the quality of systematic coverage).
This suggests that the three invariants correspond to orthogonal challenges, supporting our theoretical characterization.
