% appendix_a.tex — Implementation Details
\appendix
\section{Implementation Details}
\label{app:implementation}

\subsection{System Architecture}

The framework is implemented in Python 3.11+ using only NumPy, SciPy, and matplotlib as external dependencies.
The codebase is organized into the following modules:

\begin{itemize}
    \item \texttt{src/core/}: Type definitions, encoding interfaces, coupling model, configuration, and utilities.
    \item \texttt{src/data/}: Synthetic data generators for the BevCo scenario (sales, elasticities, policies, expert beliefs).
    \item \texttt{src/encoding/}: Statistical profile, constraint vector, temporal belief, and cross-encoder implementations.
    \item \texttt{src/agents/}: Five diagnostic agents (elasticity, interaction, constraint, temporal, portfolio).
    \item \texttt{src/synthesis/}: Causal assembler that merges evidence packets into candidate interventions.
    \item \texttt{src/quality/}: Multi-dimensional quality gate with configurable scoring weights.
    \item \texttt{src/pipeline/}: Pipeline orchestrator and ablation runner.
    \item \texttt{src/experiments/}: Four experimental modules and a master runner.
\end{itemize}

\subsection{Hyperparameters}

\begin{tabular}{ll}
\toprule
\textbf{Parameter} & \textbf{Value} \\
\midrule
Number of SKUs & \NSKUS{} \\
Number of stores & \NSTORES{} \\
Number of weeks & \NWEEKS{} \\
Elasticity noise $\sigma$ & 0.15 \\
Sales noise $\sigma$ & 0.10 \\
Random seed & 42 \\
Quality gate top-$K$ & 10 \\
Confidence decay rate & 0.1 per month \\
\bottomrule
\end{tabular}

\subsection{Reproducibility}

All experiments are deterministic given the random seed (42).
The full experiment suite completes in under 60 seconds on a modern CPU.
Code and data are available at the project repository.
